Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-05-31 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd
Minor modifications

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=10, fig.width=15}
# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.TissueOther_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueOther_ACC",
                                     "Dx.TissueOther_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueOther_DLPFC",
                                     "0.5*Dx.TissueSCZ_DLPFC+0.5*Dx.TissueSCZ_ACC-0.5*Dx.TissueControl_DLPFC-0.5*Dx.TissueControl_ACC",
                                     "0.5*Dx.TissueSCZ_DLPFC+0.5*Dx.TissueControl_DLPFC-0.5*Dx.TissueSCZ_ACC-0.5*Dx.TissueControl_ACC"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = TRUE) %>%
    rownameToFirstColumn('ensembl_gene_id') 
}, FIT.CONTR) 
names(DE) = gsub('Dx.Tissue', '', colnames(contrast))
names(DE)[7:8] = c('SCZ_ALL-Control_ALL', 'ALL_DLPFC-ALL_ACC')

@@

>>>>

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=10, fig.width=15}
# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.TissueOther_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueOther_ACC",
                                     "Dx.TissueOther_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueOther_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueSCZ_ACC",
                                     "Dx.TissueControl_DLPFC-Dx.TissueControl_ACC",
                                     "0.5*Dx.TissueSCZ_DLPFC+0.5*Dx.TissueSCZ_ACC-0.5*Dx.TissueControl_DLPFC-0.5*Dx.TissueControl_ACC",
                                     "0.5*Dx.TissueSCZ_DLPFC+0.5*Dx.TissueControl_DLPFC-0.5*Dx.TissueSCZ_ACC-0.5*Dx.TissueControl_ACC"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = TRUE) %>%
    rownameToFirstColumn('ensembl_gene_id') 
}, FIT.CONTR) 
names(DE) = gsub('Dx.Tissue', '', colnames(contrast))
names(DE)[9:10] = c('SCZ_ALL-Control_ALL', 'ALL_DLPFC-ALL_ACC')

@@

### Source Code
[R markdown](`r thisFile`)
